Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-05-25 paper_jasa.tex
power questions

\begin{dfn}\label{dfn:test}
The \textbf{visual test}, $V_{\theta}$, is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if `enough' observers select the observed data plot in the lineup of $m$ plots, and
\item \textbf{Fail to reject} $H_0$  otherwise. %if the observer selects a null plot.
\end{itemize}
where `enough' observers is defined as some threshold $x_{1-\alpha}$, for which $P(X \ge x_{1-\alpha}) < \alpha$, the level of significance.
\end{dfn}

@@

\begin{dfn} \label{dfn:power}
The \textbf{power} of a visual test $V_{\theta}$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_V(\theta)= 
        \begin{cases} 
              \frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}

>>>>

\begin{dfn}\label{dfn:test}
\red{why do we need the $\theta$? - it's not defined and not explained. usually we would assume that lineups are non-parametric}
The \textbf{visual test}, $V_{\theta}$, is defined to be 
\begin{itemize}\itemsep-3pt
\item \textbf{Reject} $H_0$ if `enough' observers select the observed data plot in the lineup of $m$ plots, and
\item \textbf{Fail to reject} $H_0$  otherwise. %if the observer selects a null plot.
\end{itemize}
where `enough' observers is defined as some threshold $x_{1-\alpha}$, for which $P(X \ge x_{1-\alpha}) < \alpha$, the level of significance.
\end{dfn}

@@

\red{How are $\Theta_0$ and $\Theta^c_0$ defined? - why do we need them? wouldn't it be better to re-formulate power in terms of acceptance region, not in terms of the parameter space?}
\begin{dfn} \label{dfn:power}
The \textbf{power} of a visual test $V_{\theta}$ is defined as the probability to reject the null hypothesis for a given parameter value $\theta$:
    \begin{equation*}
      \text{Power}_V(\theta)= 
        \begin{cases} 
              \frac1m & \text{if $\theta \in \Theta_0$,} \\
              Pr(\text{Reject } H_0) &\text{if $\theta \in \Theta^c_0$.}
        \end{cases}
    \end{equation*}
\end{dfn}
